Parallelizing Linear Recurrent Neural Nets Over Sequence Length

### 2018-04-24 poster/main.tex
Little rearrangement

\begin{block}{Beating CuDNN: Synthetic Data}

@@

\begin{block}{Accelerating existing linear RNNs}
  We implemented several recent linear RNNs with the parallel linear
  recurrence kernel, as well as a variant with purely serial evaluation.
  We were able to obtain significant speedups with parallel evaluation
  in all the architectures at longer sequence lengths.

>>>>

\begin{block}{Accelerating Existing Models}
  We implemented several recent linear RNNs with the parallel linear
  recurrence kernel, as well as a variant with purely serial evaluation.
  We were able to obtain significant speedups with parallel evaluation
  in all the architectures at longer sequence lengths.

@@

\begin{block}{Synthetic Long-Term Dependency}
